Generation of TypeScript Declaration Files from JavaScript Code

### 2021-06-02 mplr-2021/main.tex
Add new page for appendix

\appendix
\section{Results}
\subsection{Templates}
\label{sec:appendix-results-templates}
\subsubsection{module-function}
\figref{fig:experiments-results-module-function} shows the generated
declaration files for simple modules like \texttt{abs},
\texttt{dirname-regex}, and \texttt{escape-html}. All of them were
generated using the \textbf{module-function} template.

@@

\subsection{Errors in DefinitelyTyped}
\label{sec:errors-definitely-typed}
For module \texttt{glob-base} the parameter
\texttt{basePath} is declared as optional in DefinitelyTyped. However, when invoking the
function without the \texttt{basePath} parameter, an error is thrown at run time. The file generated by
\texttt{dts-generate} does not mark this parameter as optional, as shown in
\figref{fig:experiments-results-module-glob-base}. Function return type interfaces are
not inferred by \texttt{dts-generate}.

\begin{lstlisting}[
  caption={Code example for \texttt{smart-truncate} module exporting a function},
  label=code:experiments-results-module-smart-truncate,
  language=JavaScript,captionpos=b,numbers=none
  ]
  var smartTruncate = require('smart-truncate');

@@

>>>>

\clearpage
\appendix
\section{Results}
\subsection{Templates}
\label{sec:appendix-results-templates}
\subsubsection{module-function}
\figref{fig:experiments-results-module-function} shows the generated
declaration files for simple modules like \texttt{abs},
\texttt{dirname-regex}, and \texttt{escape-html}. All of them were
generated using the \textbf{module-function} template.

@@

\subsection{Errors in DefinitelyTyped}
\label{sec:errors-definitely-typed}

\begin{lstlisting}[
  caption={Code example for \texttt{smart-truncate} module exporting a function},
  label=code:experiments-results-module-smart-truncate,
  language=JavaScript,captionpos=b,float,numbers=none
  ]
  var smartTruncate = require('smart-truncate');

@@

For module \texttt{glob-base} the parameter
\texttt{basePath} is declared as optional in DefinitelyTyped. However, when invoking the
function without the \texttt{basePath} parameter, an error is thrown at run time. The file generated by
\texttt{dts-generate} does not mark this parameter as optional, as shown in
\figref{fig:experiments-results-module-glob-base}. Function return type interfaces are
not inferred by \texttt{dts-generate}.
